---
title: "Central Limit Theorem"
author: "Dongli Liu"
date: "2015Äê9ÔÂ23ÈÕ"
output: 
  pdf_document: 
    latex_engine: xelatex
---

This document is to investigate the exponential distribution in R and compare it with the Central Limit Theorem. As requested by the instructor, pre-conditions are:   
1. Set *lambda = 0.2* for all of the simulations;   
2. Investigate the distribution of averages of 40 exponentials;   
3. do a thousand simulations.   

Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponentials.  We need to:    
1. Show the sample mean and compare it to the theoretical mean of the distribution;   
2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution;      
3. Show that the distribution is approximately normal.      

Here we do this step by step. Firstly let's set  *lambda = 0.2*
```{r}
lambda <- 0.2
```

Then theoretically, for a distribution of averages of 40 exponentials, mean is:
```{r}
1/lambda;
```
standard deviation is:
```{r}
(1/lambda)/(40)^0.5;
```

Now is the simulation parts: 
```{r}
set.seed(923) # So that we could reproduce this result
mns = NULL
for (i in 1: 1000) mns = c(mns, mean(rexp(40, rate=lambda)))
```

It is easy to see that sample mean is nearly same as theoretical mean: 
```{r}
mean(mns)
```

And for sample standard deviation:
```{r}
sd(mns)
```

Next, let's have a look at the histogram of this distribution:
```{r}
hist(mns, breaks=20)
```

We could see that the histogram is quite different with  distribution of 1000 random exponentials; instead, it is much more like a Gaussian distribution via normal Q-Q plot:
```{r}
par(mfrow = c(1,2))
hist(rexp(1000))
qqnorm(mns)
```

