---
title: "Regression Analysis"
author: "Dongli Liu"
date: "2015Äê9ÔÂ24ÈÕ"
output: 
  pdf_document: 
    latex_engine: xelatex
---

As requested in course project of Regression Models, this analysis is to answer following two questions:    
1. "Is an automatic or manual transmission better for MPG"       
2. "Quantify the MPG difference between automatic and manual transmissions"

Let's first have a look at `mtcars` data set.
```{r}
attach(mtcars)
summary(mtcars)
```

Which means the variable stands for transmission type shall be changed to factor:
```{r}
mtcars$am <- factor(mtcars$am, levels = c(0, 1), labels = c("automatic", "manual"))
```

Now it is fine for further analysis:
```{r}
summary(mtcars$am)
```

Through following box-plot, we could feel there may be a difference between *manual* and *automatic* transmissons:
```{r}
plot(mtcars$am, mtcars$mpg)
```

To answer those two questions formally, we could adopt a standard regression anlysis process, while `mpg` as the response and `am` as the input:
```{r}
fit <- lm(mpg~am, data=mtcars)
summary(fit)
```

How could we interpret this result?    
1. We could see the *Coefficient* for `ammanual` is positive and statistical significant, means manual is better than automatic transmission for MPG.    
2. And the quantified MPG difference between automatic and manual transmissions is:
```{r}
summary(fit)$coef[2,1]
```
